Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/results-regression.tex
Started modifying regression section, added codings for data types.

\begin{table}
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 255.0 & 1 & 18,477.5\\
\hline
(Intercept) & 78.4 & 1 & 18,122.9\\
Device & 400.3 & 1 & \\
\hline
(Intercept) & 289.1 & 1 & 17,667.5\\
IUIPC (covariate) & 368.5 & 1 & \\
\hline
(Intercept) & 297.8 & 1 &17,383.6\\
Data Recipient & 913.4 & 4 & \\
\hline
(Intercept) & 374.6 & 1 & 14,794.5\\
Data Type & 1,866.5 & 77 & \\
\hline
(Intercept) & 303. & 1 & 13,942.9\\
Device & 11.1 & 1 &  \\
Data Recipient & 624.6 & 3 & \\
Data Type & 1,961.2 & 76 &  \\
\hline
(Intercept) & 28.4 & 1 & 12,752.8 \\
Device  & 8.8 & 1 &  \\
Data Recipient & 577.8 & 3 & \\
Data Type & 1,752.1 & 76 & \\
IUIPC (covariate) & 378.7 & 1 & \\
\hline
\end{tabular}
\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model.}
\label{regression}
\end{table}

We created several models using our three dependent variables as factors: device (smartphone vs. wearable), data recipient, and data type. We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores. Thus, we opted to remove the other covariates from our analysis.

Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit). As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor. Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device).

>>>>

\begin{table}[t]
\centering
\begin{tabular}{|l| r| r| r|}
\hline
Parameters & $\chi^2$ & $df$ & QIC\\
\hline
\hline
(Intercept) & 254.5 & 1 & 18,699.82\\
\hline
(Intercept) & 79.2 & 1 & 18,347.6\\
Device & 391.0 & 1 & \\
\hline
(Intercept) & 232.1 & 1 & 17.897.0\\
IUIPC (covariate) & 368.5 & 1 & \\
\hline
(Intercept) & 298.2 & 1 &17,606.5\\
Data Recipient & 900.0 & 4 & \\
\hline
(Intercept) & 370.9 & 1 & 14,970.7\\
Data Type & 1,898.4& 76 & \\
\hline
(Intercept) & 79.2 & 1 & 18,349.9\\
Device & 391.0 & 1 & \\
\hline
(Intercept) & 29.2 & 1 & 14,114.8\\
Device & 8.1 & 1 &  \\
Data Recipient & 579.3 & 3 & \\
Data Type & 1,765.4 & 76 &  \\
\hline
(Intercept) & 298.0 & 1 & 12,931.6 \\
Device  & 10.4 & 1 &  \\
Data Recipient & 626.2 & 3 & \\
Data Type & 1,997.5 & 76 & \\
IUIPC (covariate) & 374.8 & 1 & \\
\hline
\end{tabular}
\caption{Goodness-of-fit metrics for various binary logistic models of our data using general estimating equations to account for repeated measures. The columns represent the Wald test statistic for each parameter and the overall Quasi-Akaike Information Criterion (QIC) for each model. Each parameter listed was statistically significant at $p<0.0005$.}
\label{regression}
\end{table}

We created several models using our three dependent variables as factors: device (smartphone vs. wearable), data recipient, and data type. We also used our collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these eight parameters and observed that the only covariate that had an observable effect on our models was participants' IUIPC scores. Thus, we opted to remove the other covariates from our analysis. Similarly, we observed no statistically significant interaction effects between any of these four variables, which is why we did not include them in our models.

Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection (lower relative values indicate better fit). As can be seen, while the remaining four predictors all contributed to the predictive power of our model, the data type was the strongest predictor. Conversely, despite being significant, the device was the weakest predictor (i.e., whether participants were answering questions about a smartphone or a wearable device). This suggests that participants' biases towards specific wearable devices or wearable devices in general had a minimal effect on their results, and that they were primarily focused on the data type captured and how it will be shared.

### 2015-03-04 tex-inputs/results-type.tex
Started modifying regression section, added codings for data types.

>>>>

The data types the we examined span several existing and future use cases. However, we do not necessarily believe they are comprehensive or cover all possible future use cases for how wearable devices might capture personal data. As such, we decided to code each data type in terms of both the capture medium (e.g., video, audio, text, etc.) and the type of risk to which it might expose the user. The purpose of this was to examine {\it why} participants viewed certain data types as more or less risky than others so that we can then generalize our results to other data types that were not covered by this particular survey instrument. To this end, two researchers agreed on a codebook and then independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.} in terms of the medium used for collection and in terms of the type of risk posed to the user. The mediums fell into six possible categories:

\begin{enumerate}
\item Photo
\item Video
\item Audio
\item Behavioral Information
\item Biometric Information
\item Demographic Information
\end{enumerate}

The associated risks with each data type fell into the following five categories:

\begin{enumerate}
\item {\bf Financial:} The risk involves the loss of money or property.
\item {\bf Image:} The risk involves loss of control over one's self-image (e.g., publicizing something embarrassing).
\item {\bf Medical:} The risk involves disclosure of medical information.
\item {\bf Physical:} The risk involves physical harm to the user.
\item {\bf Relationships:} The risk involves damage to the user's inter-personal relationships.
\end{enumerate}

Upon independently coding each data type along these two axes, the researchers met to resolve any disagreements, such that the resulting codings reflected unanimity. Prior to this resolution, they agree on 83\% of the codings. Cohen's $\kappa$ was 0.75 for the risks and 0.81 for the mediums, both indicating ``excellent'' agreement~\cite{Fleiss2003}.
